Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-07 doc/slides/hong+eisner.TLT13.slides.tex
fixed typos

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for building new parsers
  \end{itemize}
}

@@

\subsection{Relativization}
\frame{\frametitle{Relativization}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        The \& boy \& that \& Jill \& skipped \& with \& fell \& down \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 1.5ex]{7}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{5}{}
      \depedge[edge above, thick, hide label]{5}{4}{}
      \depedge[edge above, thick, hide label]{5}{6}{}
      \depedge[edge above, thick, hide label, edge unit distance = 1.8ex]{7}{2}{}
      \depedge[edge above, thick, hide label]{7}{8}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{6}{2}{}
    \end{dependency}
    \caption*{The boy is the object of ``with'' as well as the subject of ``fell''.}
  \end{figure}
}

@@

    \end{dependency}
    \caption*{Jack and Jill serve as the two arguments to and, but they are also semantically subjects of went.}
  \end{figure}
}

>>>>

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
  \end{itemize}
}

@@

\subsection{Relativization}
\frame{\frametitle{Relativization}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        The \& boy \& that \& Jill \& skipped \& with \& fell \& down \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 1.5ex]{7}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{5}{}
      \depedge[edge above, thick, hide label]{5}{4}{}
      \depedge[edge above, thick, hide label]{5}{6}{}
      \depedge[edge above, thick, hide label, edge unit distance = 1.8ex]{7}{2}{}
      \depedge[edge above, thick, hide label]{7}{8}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{6}{2}{}
    \end{dependency}
    \caption*{The boy is the object of \textit{with} as well as the subject of \textit{fell}.}
  \end{figure}
}

@@

    \end{dependency}
    \caption*{Jack and Jill serve as the two arguments to \textit{and}, but are also subjects of \textit{went}.}
  \end{figure}
}
